Neuroecon Poster Figures

### 2017-10-05 code/NeuroeconPoster.Rmd
added printed version of the neuroecon poster

ggsave('Lit_Review_Poster_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)
```

```{r}
p4_t <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)

>>>>

ggsave('Lit_Review_Poster_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
```

```{r}
p4_t <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
